\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[top=0.5in, bottom=0.5in, left=0.75in, right=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome} % For icons
\usepackage{graphicx}    % For resizing icons
\usepackage{multicol}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{*1}{*1}

\begin{document}

\begin{center}
    {\LARGE \textbf{PENG HAO}} \\

    \faHome\ \href{https://www.linkedin.com/in/peng-hao-phd}{https://www.linkedin.com/in/peng-hao-phd} \\[1em]

    % Phone Icon and Phone Number
    \faPhone\ \href{tel:+61416125616}{+61416125616} 
    \quad  % Add some space
    % Email Icon and Email Address
    \faEnvelope\ \href{mailto:haopengbuaa@gmail.com}{haopengbuaa@gmail.com}
    \quad % Add some space      
    % GitHub Icon and GitHub URL
    \faGithub\ \href{https://github.com/transferhp}{https://github.com/transferhp}
\end{center}

\vspace{0.5em}

\begin{center}
    \textbf{\large Experience} \\
    \rule{\textwidth}{0.1pt}
\end{center}

\noindent
\textbf{Slalom Build} \hfill Sydney, AU \\
\textit{Machine Learning Architect} \hfill May. 2022 – Present \\
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \item Architected and developed a scalable, reproducible model training pipeline on AzureML for a transportation client, addressing complex object detection challenges.
    \item Designed and deployed a serverless Generative AI solution on AWS for a legal client, significantly enhancing productivity in analyzing customer survey data.
    \item Delivered a comprehensive end-to-end MLOps solution for a manufacturing client using AWS SageMaker and GitHub Actions, leveraging Terraform for automated infrastructure provisioning.
    \item Refactored model training code using Ray distributed framework on GCP for a retail client, reducing the training time by 3x.
    \item Led technical solution design for clients and mentored junior engineers.
\end{itemize}

\vspace{0.5em}

\noindent
\textbf{Endeavour Group} \hfill Sydney, AU \\
\textit{Senior Data Scientist} \hfill Nov. 2020 – Feb 2022 \\
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \item Managed and maintained a recommendation model for a major Australian liquor brand, driving personalized offer emails to millions of customers.
    \item Analyzed model performance and email campaign effectiveness, providing recommendations for model optimization.
    \item Integrated MLflow into the existing ML pipeline to enhance experiment tracking, enabling rapid iteration and efficient model development and deployment for data scientists.
\end{itemize}

\vspace{0.5em}

\noindent
\textbf{Elula} \hfill Sydney, AU \\
\textit{Data Scientist} \hfill Jun. 2018 – Nov 2020 \\
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \item Developed a scalable data quality check tool using PySpark to handle billion-record datasets and detect data drift prior to model training.
    \item Designed and customized predictive models for customer churn prediction.
    \item Engineered automated ETL pipelines (Python, AWS) for efficient data analysis workflows.
\end{itemize}

\vspace{0.5em}

\begin{center}
    \textbf{\large Professional Certifications} \\
    \rule{\textwidth}{0.1pt}
\end{center}

\noindent
\begin{multicols}{2}
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \item AWS Certified Mahicne Learning - Specialty
    \item Databricks Certified Generative AI Engineer Associate
    \item Databricks Certified Machine Learning Professional
    \item Google Cloud Professional Machine Learning Engineer
    \item Google Cloud Professional Data Engineer
    \item Google Cloud Professional Cloud Developer
\end{itemize}
\end{multicols}

\vspace{0.5em}

\begin{center}
    \textbf{\large Skills} \\
    \rule{\textwidth}{0.1pt}
\end{center}
Machine Learning, MLOps, GenAI, AWS SageMaker, AWS Bedrock, AzureML, Vertex AI, Python, DevOps

\vspace{0.5em}

\begin{center}
    \textbf{\large Education} \\
    \rule{\textwidth}{0.1pt}
\end{center}

\noindent
\textbf{University of Technology Sydney, Computer Science} \hfill Sydney, AU \\
\textit{Doctor of Philosophy} \hfill Dec. 2017 \\
\begin{itemize}[leftmargin=0.15in, itemsep=1pt]
    \item Thesis: Cross-domain Recommender Systems through Tag-based Models
\end{itemize}

\end{document}
